Empirical Analysis of Performance Bottlenecks in Graph Neural Network Training with GPUs

### 2020-12-23 NEUROC/Response-MajRev/response_letter.tex

% !TEX program=pdflatex
% LaTeX rebuttal letter example. 
% 
% Copyright 2019 Friedemann Zenke, fzenke.net
%
% Based on examples by Dirk Eddelbuettel, Fran and others from 
% https://tex.stackexchange.com/questions/2317/latex-style-or-macro-for-detailed-response-to-referee-report
% 
% Licensed under cc by-sa 3.0 with attribution required.

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{lipsum} % to generate some filler text
\usepackage{fullpage}
\usepackage{times}
\usepackage{amsmath, amsthm, amsfonts}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage{multirow}
\usepackage{lscape}
\usepackage{xcolor}
\usepackage{float}
\usepackage{subfig}
\usepackage{graphicx}
\usepackage{framed}
% Vector
\newcommand{\MyVec}[1]{\boldsymbol{#1}}
% Matrix
\newcommand{\MyMat}[1]{\boldsymbol{#1}}
% Vectors with hat
\newcommand{\hvec}[1]{\hat{\boldsymbol{h}}_{#1}}
% Model parameters
\newcommand{\Param}[1]{\textcolor{blue}{#1}}

\newenvironment{myquote}%
{\begin{leftbar}\begin{quote}}
{\end{quote}\end{leftbar}}

@@

    In the revised manuscript, we use $e_{x,y}$ to represent an edge and use $\boldsymbol{e}_{x,y}$ to represent its input feature vector.
    %
    The input feature vectors of all edges are same for all GNN layers.
    %
    We use $\boldsymbol{s}$ to represent aggregated vectors outputted by the aggregation function $\Sigma$ in graph neurons.
    %
    For every vertex $v_x$, we use $\boldsymbol{s}^l_x$ to denote its aggregated vector in the GNN layer $l$.
    %
    If the GNN layer $l$ has sub-layers, $\boldsymbol{s}^{l,i}_x$ represents its aggregated vector in the $i$-th sub-layer.

    To clarify the concept of \emph{sub-layers} in a GNN layer, we have added more description on it in the revised manuscript.
    %
    We first introduce the concept of sub-layer in Section 2.2 ``Graph Neuron and Message-passing Model'' as:
    %
    \begin{myquote}
        Some complex GNNs like GAT [6] and GaAN [7] use more than one message passing phase in each GNN layer.
        %
        We regard every message passing phase in a GNN layer as a \emph{sub-layer}.
        %
        We will give out more details on sub-layers when we introduce GAT.
    \end{myquote}
    %
    We then use GAT as an example to elaborate on the concept of sub-layers in Section 2.3 ``Representative GNNs'' as:
    %
    \begin{myquote}
        \newcommand{\GATCalcWeight}{\exp(LeakyReLU(\Param{\MyVec{a}}^T[\hvec{y}[k] \parallel \hvec{x}[k]]))}
        Each GAT layer consists of a vertex pre-processing phase and two sub-layers (i.e., message-passing phases).

@@

% R1Q2
\begin{point}
    Some typical applications of GNNs should be included, such as video object segmentation [ref1], human-object interaction [ref2] and human-parsing [ref3].[1] Zero-shot video object segmentation via attentive graph neural networks,iccv 2019 [2] Learning human-object interactions by graph parsing neural networks, eccv 2018. [3] Hierarchical human parsing with typed part-relation reasoning, cvpr 2020.
\end{point}

\begin{reply}
	Thank you for pointing out our shortcomings. Computer vision is indeed another important application area of graph neural networks. We have added the mentioned references in the INTRODUCTION section in the revised manuscript. We quote the related sentence below:
    \begin{myquote}
         The powerful expression ability makes GNNs achieve good accuracy in not only graph analytical tasks [8, 9, 10] (like node classification and link prediction) but also computer vision tasks (like human-object interaction [11], human parsing [12], and video object segmentation [13]).
    \end{myquote}
\end{reply}

@@

\end{reply}

% R1Q4
\begin{point}
    Figures 6 and 7 should be adjusted. The figures and fonts are too small.
\end{point}

\begin{reply}

    Thank you for pointing the problem out.
    %
    Besides Figure 6 and Figure 7, we have adjusted all the figures in the revised manuscript to make sure that font sizes in figures are no less than the font size of figure captions.
    %
    To make the figures more easy to read, we also splitted Figure 6 and Figure 7 into five figures (Figure 6 to 10) in the revised manuscript to enlarge the subfigures.

@@

    And the experimental evaluation were done over 6 large graph-structured datasets.
\end{point}

\begin{reply}
    Thank you very much for your appreciation.	
\end{reply}

% R2Q3
\begin{point}
    While, one major drawback is that I did not clearly see the analysis complexity v.s. accuracy. For example, in Figure 19 and 20, I did not see network accuracy from those 4 GNNs. There is always tradeoff between model complexity and model performance, and in some scenarios where high complexity is allowed, a sophisticated model of more powerful representation capability is still needed.
\end{point}

\begin{reply}
    Thanks very much for your valuable suggestions.
    %
    The model complexity directly affected both the accuracy and the training time.
    %
    In order to analyze the relationship between model complexity and accuracy, we conducted two kinds of extra experiments in the revised manuscript: (1) how the hyper-parameters of the GNNs (like the dimension of hidden vectors and the number of heads) affected the accuracy of GNNs; (2) how the batch size in the sampling methods affected the accuracy of GNNs.

    In this reply, we focus on the first kind of experiments.
    %
    We will introduce our results of the second kind of experiments in the next reply.

    In the revised manuscript, we added an extra paragraph ``Effects on Accuracy'' at the end of Section 4.1 ``Effects of Hyper-parameters on Performance'' to analyze how the hyper-parameters affect the accuracy.
    %
    We had two main findings: (1) the accuracy of GNNs was much more sensitive to the dimension of hidden vectors $dim(\MyVec{h}^1_x)$ (for GCN/GGNN/GaAN) and the dimension of each head $d_{head}$ (for GAT) than the other hyper-parameters; (2) the relative accuracy between the four typical GNNs varied greatly with different datasets.
    %
    We quote the related paragraphs from the revised manuscript below:

    \begin{myquote}
            %%% TO ADD QUOTE %%%
    \end{myquote}
\end{reply}

### 2020-12-23 NEUROC/sec4-experiments.tex

The relationship between hyper-parameters of GNNs (i.e., model complexity) and accuracy is very complicated, and there is no clear theoretical analysis yet.
%
Generally speaking, higher model complexity can bring stronger expressive ability and may bring higher accuracy, but it also increases the risk of overfitting.
%
To evaluate the effects of hyper-parameters on accuracy, we measured the accuracy of the four typical GNNs under different hyper-parameters.
%
\figurename~\ref{fig:exp_hyperparameter_accuracy} shows the experimental results.

>>>>

The relationship between hyper-parameters of GNNs (i.e., model complexity) and accuracy is very complicated, and there is no clear theoretical analysis yet.
%
Generally speaking, higher model complexity can bring powerful representation capability and may bring higher accuracy, but it also increases the risk of overfitting.
%
To evaluate the effects of hyper-parameters on accuracy, we measured the accuracy of the four typical GNNs under different hyper-parameters.
%
\figurename~\ref{fig:exp_hyperparameter_accuracy} shows the experimental results.
